Reproducible development environments with rix

### 2024-10-01 paper.qmd
Update paper.qmd

@peng2011 introduced the idea of reproducibility being on a continuum: on one of
the ends of this continuum, we only have access to the paper describing the
studies, which is not reproducible at all. If in addition, to this paper authors
make the original source code of the analysis available, reproducibility is
improved, albeit only by a little. Adding the original data improves
reproducibility yet again. Finally, if to all this the authors add what Roger
Peng named the *linked and executable code and data*, we reach the gold standard
of reproducibility.

@@

```{r, eval = F}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    exec_mode = "non-blocking",
    project_path = path_subshell,
    message_type = "simple"
  )

@@

```{r, include = FALSE}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    exec_mode = "non-blocking",
    project_path = path_subshell,
    message_type = "simple"
  )

>>>>

@peng2011 introduced the idea of reproducibility being on a continuum: on one of
the ends of this continuum, we only have access to the paper describing the
studies, which is not reproducible at all. If in addition to this paper authors
make the original source code of the analysis available, reproducibility is
improved. Adding the original data improves reproducibility yet again. 
Finally, if to all this the authors add what Roger
Peng named the *linked and executable code and data*, we reach the gold standard
of reproducibility.

@@

```{r, eval = F}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    project_path = path_subshell,
    message_type = "simple"
  )

@@

```{r, include = FALSE}
out_subshell <- with_nix(
    expr = function(){
      set.seed(1234)
      a <- sample(seq(1, 10), 5)
      set.seed(NULL)
      return(a)
    },
    program = "R",
    project_path = path_subshell,
    message_type = "simple"
  )
